%!TeX program = pdflatex
% Geoff Boeing's Curriculum Vitae
% Email: boeing@usc.edu
% Web: https://geoffboeing.com/
% Repo: https://github.com/gboeing/cv

\documentclass[11pt,letterpaper]{report}

\usepackage[T1]{fontenc} % output T1 font encoding (8-bit) for accented characters as single glyph
\usepackage[strict,autostyle]{csquotes} % smart and nestable quote marks
\usepackage[USenglish]{babel} % regionalize hyphens, quote marks, etc automatically
\usepackage{microtype}% improve text appearance with kerning, etc
\usepackage{datetime} % enable formatting of date output
\usepackage{tabto}    % make nice tabbing
\usepackage{setspace} % custom line spacing
\usepackage{hyperref} % enable hyperlinks and pdf metadata
\usepackage{geometry} % manually set page margins
\usepackage{enumitem} % enumerate with [resume] option
\usepackage{titlesec} % allow custom section fonts
\usepackage{xcolor}

% what is your name?
\newcommand{\myname}{Zaibei (Eric) Li}

% select default typefaces
\usepackage{ebgaramond} % document's serif typeface
\usepackage{tgheros}    % document's sans serif typeface

% how far to tab for list items with left-aligned date: different fonts need different widths
\newcommand{\listtabwidth}{1.7cm}

% define font to use as document's title
\newcommand{\namefont}[1]{{\normalfont\bfseries\Huge{#1}}}

% set section heading fonts and before/after spacing
\SetTracking{encoding=*, family=\sfdefault}{30} % increase sans serif headings tracking
\titleformat{\section}{\lsstyle\sffamily\small\bfseries\uppercase}{}{}{}{}
\titlespacing{\section}{0pt}{30pt plus 4pt minus 4pt}{8pt plus 2pt minus 2pt}

% set subsection heading fonts and before/after spacing
\titleformat{\subsection}{\lsstyle\sffamily\footnotesize\bfseries}{}{}{}{}
\titlespacing{\subsection}{0pt}{16pt plus 4pt minus 4pt}{4pt plus 2pt minus 2pt}

% set page margins (assumes letter paper)
\geometry{body={6.5in, 9.0in},
    left=1.0in,
    top=1.0in}

% prevent paragraph indentation
\setlength\parindent{0em}

% set line spacing
\setstretch{0.9}

% define space between list items
\newcommand{\listitemspace}{0.25em}

% make unordered lists without bullets and use compact spacing
\renewenvironment{itemize}
{\begin{list}{}{\setlength{\leftmargin}{0em}
                \setlength{\parskip}{0em}
                \setlength{\itemsep}{\listitemspace}
                \setlength{\parsep}{\listitemspace}}}
{\end{list}}

% make tabbed lists so content is left-aligned next to years
\TabPositions{\listtabwidth}
\newlist{tablist}{description}{3}
\setlist[tablist]{leftmargin=\listtabwidth,
    labelindent=0em,
    topsep=0em,
    partopsep=0em,
    itemsep=\listitemspace,
    parsep=\listitemspace,
    font=\normalfont}

% print only the month and year when using \today
\newdateformat{monthyeardate}{\monthname[\THEMONTH] \THEYEAR}

% define hyperlink appearance and metadata for pdf properties
\hypersetup{
    colorlinks  = true,
    urlcolor    = black,
    citecolor   = black,
    linkcolor   = black,
    pdfauthor   = {\myname},
    pdfkeywords = {multimodal learning analytics, Human-AI collaboration, IoT, ubiquitous computing},
    pdftitle    = {\myname: Curriculum Vitae},
    pdfsubject  = {Curriculum Vitae},
    pdfpagemode = UseNone
}

\begin{document}
    \raggedright{}

    % display your name as the document title
    \namefont{\myname}

    % affiliation and contact info blocks
    \vspace{1em}
    \begin{minipage}[t]{0.700\textwidth}
        % current primary affiliation, left-aligned
        Human-Centered Computing\\
        Department of Computer Science\\
        University of Copenhagen
    \end{minipage}
    \begin{minipage}[t]{0.295\textwidth}
        % contact info details, right-aligned
        \flushright{}
        \href{mailto:zali@di.ku.dk}{zali@di.ku.dk} \\
        +45 91858214 \\
        \href{https://lizaibeim.github.io}{lizaibeim.github.io}
    \end{minipage}
    

    \section*{Research Profile}

    I am a Doctoral Researcher at the University of Copenhagen, specializing in multimodal data analytics and human-centered AI systems. My research bridges multimodal wearable sensing, human-AI collaboration, and ubiquitous computing. I design and build IoT-based systems and interactive dashboards to model and visualize complex collaborative behavior in real-world environments.

    \section*{Education}

    \begin{tablist}

        \item[Ph.D.] \tab{}Computer Science, University of Copenhagen, Copenhagen, 2027 (expected)
        \item[M.S.]  \tab{}Computer Science, University of Copenhagen, 2022
        \item[B.S.]  \tab{}Information Technology, Hong Kong Polytechnic University, 2019
        \item[Exchange]  \tab{}Computer Science, The Korea Advanced Institute of Science and Technology, 2017

    \end{tablist}

    \section*{Research Experience}

    \noindent \textbf{Hiroshima City University} \hfill Hiroshima, Japan \\
    \textit{Visiting Researcher} \hfill Nov 2025--Jan 2026
    \begin{list}{\textbullet}{\setlength{\leftmargin}{1.2em}
                   \setlength{\labelsep}{0.5em}
                   \setlength{\itemsep}{\listitemspace}
                   \setlength{\parsep}{\listitemspace}}
        \item Prototyped a multimodal sensing setup (Arduino, mobile sensing, smart glasses); secured a research partnership with Meta \href{https://www.projectaria.com/}{Project Aria}.
        \item Developed CoLA (\href{https://ucph-cola.org}{ucph-cola.org}), an egocentric wearable platform integrating real-time multimodal sensing and Human-AI interaction for collaborative learning analytics.
    \end{list}
    \vspace{0.8em}

    \noindent \textbf{University of Copenhagen} \hfill Copenhagen, Denmark \\
    \textit{Doctoral Researcher} \hfill Feb 2024--Present
    \begin{list}{\textbullet}{\setlength{\leftmargin}{1.2em}
                   \setlength{\labelsep}{0.5em}
                   \setlength{\itemsep}{\listitemspace}
                   \setlength{\parsep}{\listitemspace}}
        \item Integrated prior prototypes into OpenMMLA, an IoT-based multimodal toolkit with reusable end-to-end data pipelines for collaborative learning analytics.
        \item Developed interactive workflows and pipeline components for multimodal sensing, optimizing data synchronization, sensor fusion, and interpretable behavioral analysis.
    \end{list}
    \vspace{0.8em}

    \noindent \textbf{University of Copenhagen} \hfill Copenhagen, Denmark \\
    \textit{Research Assistant} \hfill Jun 2023--Feb 2024
    \begin{list}{\textbullet}{\setlength{\leftmargin}{1.2em}
                   \setlength{\labelsep}{0.5em}
                   \setlength{\itemsep}{\listitemspace}
                   \setlength{\parsep}{\listitemspace}}
        \item Prototyped sociometric badges and established early multimodal data workflows, which directly evolved into the open-source OpenMMLA toolkit.
    \end{list}


    \section*{Selected Publications}

    \begin{tablist}
        \item[2026] \tab{} \textbf{Z. Li}, V. Holm-Janas, S. Yamaguchi, and D. Spikol. \enquote{Designing for Transparency: Gaze-Augmented Collaborative Action Recognition with Vision-Language Models.} \textit{Proceedings of the 26th IEEE International Conference on Advanced Learning Technologies (ICALT '26)} \textit{[Accepted]}
        \item[2026] \tab{} \textbf{Z. Li}, Q. Li, S. Yamaguchi, and D. Spikol. \enquote{BadgeX: IoT-Enhanced Wearable Analytics Meets LLMs for Collaborative Learning.} \textit{arXiv preprint}, \href{https://arxiv.org/abs/2604.04093}{arXiv:2604.04093} \textit{[Preprint]}
        \item[2025] \tab{} \textbf{Z. Li}, S. Yamaguchi, and D. Spikol. \enquote{OpenMMLA: an IoT-based Multimodal Data Collection Toolkit for Learning Analytics.} \textit{Proceedings of the 15th Learning Analytics and Knowledge Conference (LAK '25)}, \href{https://doi.org/10.1145/3706468.3706525}{https://doi.org/10.1145/3706468.3706525} \textit{[Oral presentation]}
        \item[2024] \tab{} \textbf{Z. Li}, M. T. Jensen, A. Nolte, and D. Spikol. \enquote{Field report for Platform mBox: Designing an Open MMLA Platform.} \textit{Proceedings of the 14th Learning Analytics and Knowledge Conference (LAK '24)}, \href{https://doi.org/10.1145/3636555.3636872}{https://doi.org/10.1145/3636555.3636872} \textit{[Oral presentation]}
        \item[2024] \tab{} \textbf{Z. Li}, D. Spikol, and L. Nøhr. \enquote{mBox-audio: Unveiling Conversational Dynamics through Real-Time and Post-Time Audio Analysis for MMLA.} \textit{pp. 130-132 in Companion Proceedings 14th International Conference on Learning Analytics and Knowledge (LAK '24)}, \href{https://www.solaresearch.org/wp-content/uploads/2024/03/LAK24_CompanionProceedings.pdf}{LAK '24 Companion Proceedings} \textit{[Poster]}
    \end{tablist}


    \section*{Selected Projects}

    \begin{itemize}
    
        \item \textbf{CoLA}: An egocentric wearable platform for real-time multimodal sensing and Human-AI collaboration in team-based learning analytics, \href{https://ucph-cola.org}{\textcolor{blue}{\textit{link}}}
        \item \textbf{OpenMMLA}: An open-source multimodal data collection toolkit for collaborative learning analytics, \href{https://github.com/ucph-ccs/OpenMMLA}{\textcolor{blue}{\textit{link}}}
        \item \textbf{MotionMatching}: A real-time motion matching system on Unity implemented in C\#, \href{https://github.com/lizaibeim/motion-matching}{\textcolor{blue}{\textit{link}}}
        \item \textbf{CasperFFG}: A Python implementation of the CasperFFG consensus combined with PoW consensus on simulated blockchain, \href{https://github.com/lizaibeim/casper-ffg}{\textcolor{blue}{\textit{link}}}

    \end{itemize}


    \section*{Professional Employment}

    \noindent \textbf{Yonyou} \hfill Hong Kong, China \\
    \textit{IT Consultant} \hfill May 2019--Aug 2019
    \vspace{0.8em}

    \noindent \textbf{Sina.com} \hfill Beijing, China \\
    \textit{Data Analyst Intern} \hfill Jun 2017--Aug 2017


    \section*{Grants and Awards}

    \begin{tablist}
        \item[2025\phantom{--2027}] \tab{}Best Short Paper Award @ LAK '25
        \item[2025\phantom{--2027}] \tab{}Meta Project Aria Research Partnership / Hardware Grant
        \item[2024--2027] \tab{}PhD Fellowship, University of Copenhagen
    \end{tablist}


    \section*{Service}

    Peer reviewer: \textit{Knowledge-Based Systems}; \textit{European Conference on Technology-Enhanced Learning (EC-TEL)}


    % display today's date as Month Year after a vertical space below the end of the text
    \begin{center}
        \vfill
        Updated \monthyeardate\today
    \end{center}

\end{document}
