%!TeX program = pdflatex
% Geoff Boeing's Curriculum Vitae
% Email: boeing@usc.edu
% Web: https://geoffboeing.com/
% Repo: https://github.com/gboeing/cv

\documentclass[11pt,letterpaper]{report}

\usepackage[T1]{fontenc} % output T1 font encoding (8-bit) for accented characters as single glyph
\usepackage[strict,autostyle]{csquotes} % smart and nestable quote marks
\usepackage[USenglish]{babel} % regionalize hyphens, quote marks, etc automatically
\usepackage{microtype}% improve text appearance with kerning, etc
\usepackage{datetime} % enable formatting of date output
\usepackage{tabto}    % make nice tabbing
\usepackage{setspace} % custom line spacing
\usepackage{hyperref} % enable hyperlinks and pdf metadata
\usepackage{geometry} % manually set page margins
\usepackage{enumitem} % enumerate with [resume] option
\usepackage{titlesec} % allow custom section fonts
\usepackage{xcolor}

% what is your name?
\newcommand{\myname}{Zaibei Li}

% select default typefaces
\usepackage{ebgaramond} % document's serif typeface
\usepackage{tgheros}    % document's sans serif typeface

% how far to tab for list items with left-aligned date: different fonts need different widths
\newcommand{\listtabwidth}{1.7cm}

% define font to use as document's title
\newcommand{\namefont}[1]{{\normalfont\bfseries\Huge{#1}}}

% set section heading fonts and before/after spacing
\SetTracking{encoding=*, family=\sfdefault}{30} % increase sans serif headings tracking
\titleformat{\section}{\lsstyle\sffamily\small\bfseries\uppercase}{}{}{}{}
\titlespacing{\section}{0pt}{30pt plus 4pt minus 4pt}{8pt plus 2pt minus 2pt}

% set subsection heading fonts and before/after spacing
\titleformat{\subsection}{\lsstyle\sffamily\footnotesize\bfseries}{}{}{}{}
\titlespacing{\subsection}{0pt}{16pt plus 4pt minus 4pt}{4pt plus 2pt minus 2pt}

% set page margins (assumes letter paper)
\geometry{body={6.5in, 9.0in},
    left=1.0in,
    top=1.0in}

% prevent paragraph indentation
\setlength\parindent{0em}

% set line spacing
\setstretch{0.9}

% define space between list items
\newcommand{\listitemspace}{0.25em}

% make unordered lists without bullets and use compact spacing
\renewenvironment{itemize}
{\begin{list}{}{\setlength{\leftmargin}{0em}
                \setlength{\parskip}{0em}
                \setlength{\itemsep}{\listitemspace}
                \setlength{\parsep}{\listitemspace}}}
{\end{list}}

% make tabbed lists so content is left-aligned next to years
\TabPositions{\listtabwidth}
\newlist{tablist}{description}{3}
\setlist[tablist]{leftmargin=\listtabwidth,
    labelindent=0em,
    topsep=0em,
    partopsep=0em,
    itemsep=\listitemspace,
    parsep=\listitemspace,
    font=\normalfont}

% print only the month and year when using \today
\newdateformat{monthyeardate}{\monthname[\THEMONTH] \THEYEAR}

% define hyperlink appearance and metadata for pdf properties
\hypersetup{
    colorlinks  = true,
    urlcolor    = black,
    citecolor   = black,
    linkcolor   = black,
    pdfauthor   = {\myname},
    pdfkeywords = {multimodal learning analytics, Human-AI collaboration, IoT, ubiquitous computing},
    pdftitle    = {\myname: Curriculum Vitae},
    pdfsubject  = {Curriculum Vitae},
    pdfpagemode = UseNone
}

\begin{document}
    \raggedright{}

    % display your name as the document title
    \namefont{\myname}

    % affiliation and contact info blocks
    \vspace{1em}
    \begin{minipage}[t]{0.700\textwidth}
        % current primary affiliation, left-aligned
        Human-Centered Computing\\
        Department of Computer Science\\
        University of Copenhagen
    \end{minipage}
    \begin{minipage}[t]{0.295\textwidth}
        % contact info details, right-aligned
        \flushright{}
        \href{mailto:zali@di.ku.dk}{zali@di.ku.dk} \\
        +45 91858214 \\
        \href{https://lizaibeim.github.io}{lizaibeim.github.io}
    \end{minipage}

    \section*{Research Profile}

    Doctoral researcher in computer science working at the intersection of multimodal sensing, wearable systems, and human-centered computing. Experienced in designing and building end-to-end systems for multimodal data collection, sensor fusion, interpretable behavioral modeling, and interactive AI applications.

    \section*{Education}

    \begin{tablist}
        \item[Ph.D.] \tab{}Computer Science, University of Copenhagen, Copenhagen, 2027 (expected)
        \item[M.S.]  \tab{}Computer Science, University of Copenhagen, 2022
        \item[B.S.]  \tab{}Information Technology, Hong Kong Polytechnic University, 2019
        \item[Exchange]  \tab{}Computer Science, The Korea Advanced Institute of Science and Technology, 2017
    \end{tablist}

    \section*{Research Areas}

    \begin{itemize}
        \item Multimodal learning analytics: multimodal data collection, behavioral modeling, and collaborative learning
        \item Ubiquitous computing: IoT systems, embedded sensing, and mobile computing
        \item Human-centered computing: interpretable AI, interactive systems, and human-AI interaction
    \end{itemize}    

    \section*{Publications}

    \subsection*{Conference Proceedings}

    \begin{tablist}
        \item[2026] \tab{} \textbf{Z. Li}, V. Holm-Janas, S. Yamaguchi, and D. Spikol. \enquote{Designing for Transparency: Gaze-Augmented Collaborative Action Recognition with Vision-Language Models.} \textit{Proceedings of the 26th IEEE International Conference on Advanced Learning Technologies (ICALT '26)} \textit{[Accepted]}
        \item[2025] \tab{} \textbf{Z. Li}, S. Yamaguchi, and D. Spikol. \enquote{OpenMMLA: an IoT-based Multimodal Data Collection Toolkit for Learning Analytics.} \textit{Proceedings of the 15th Learning Analytics and Knowledge Conference (LAK '25)}, \href{https://doi.org/10.1145/3706468.3706525}{https://doi.org/10.1145/3706468.3706525}
        \item[2024] \tab{} \textbf{Z. Li}, M. T. Jensen, A. Nolte, and D. Spikol. \enquote{Field report for Platform mBox: Designing an Open MMLA Platform.} \textit{Proceedings of the 14th Learning Analytics and Knowledge Conference (LAK '24)}, \href{https://doi.org/10.1145/3636555.3636872}{https://doi.org/10.1145/3636555.3636872}
        \item[2024] \tab{} A. Ohsaki, D. Spikol, and \textbf{Z. Li}. \enquote{Combination of Computer and Human Analytics for Multimodal Learning Analysis in a Hackathon.} \textit{pp. 127--129 in Companion Proceedings 14th International Conference on Learning Analytics and Knowledge (LAK '24)}, \href{https://www.solaresearch.org/wp-content/uploads/2024/03/LAK24_CompanionProceedings.pdf}{LAK '24 Companion Proceedings}
        \item[2024] \tab{} \textbf{Z. Li}, D. Spikol, and L. Nøhr. \enquote{mBox-audio: Unveiling Conversational Dynamics through Real-Time and Post-Time Audio Analysis for MMLA.} \textit{pp. 130--132 in Companion Proceedings 14th International Conference on Learning Analytics and Knowledge (LAK '24)}, \href{https://www.solaresearch.org/wp-content/uploads/2024/03/LAK24_CompanionProceedings.pdf}{LAK '24 Companion Proceedings}
        \item[2024] \tab{} D. Spikol, \textbf{Z. Li}, A. Nolte, A. Ohsaki, and K. Rapur. \enquote{Investigating Hackathons with Collaboration Analytics.} \textit{Proceedings of the 8th International Conference on Game Jams, Hackathons and Game Creation Events (ICGJ '24)}, \href{https://doi.org/10.1145/3697789.3697797}{https://doi.org/10.1145/3697789.3697797}
        \item[2024] \tab{} H. Ouhaichi, D. Spikol, \textbf{Z. Li}, and B. Vogel. \enquote{Conceptual Design of Multimodal Learning Analytics for Spoken Language Acquisition.} \textit{Proceedings of the 19th European Conference on Technology Enhanced Learning (EC-TEL '24)}, \href{https://doi.org/10.1007/978-3-031-72312-4_19}{https://doi.org/10.1007/978-3-031-72312-4\_19}
        \item[2024] \tab{} V. Holm-Janas, O. Caro Miya Marshall, \textbf{Z. Li}, J. Bruun, and D. Spikol. \enquote{Design Framework for Multimodal Learning Analytics Leveraging Human Observations.} \textit{Proceedings of the 19th European Conference on Technology Enhanced Learning (EC-TEL '24)}, \href{https://doi.org/10.1007/978-3-031-72312-4_13}{https://doi.org/10.1007/978-3-031-72312-4\_13}
        \item[2024] \tab{} H. Ouhaichi, D. Spikol, B. Vogel, and \textbf{Z. Li}. \enquote{Analytics in Glocal Classrooms: Integrating Multimodal Learning Analytics in a Smart Learning Environment.} \textit{2024 IEEE International Conference on Advanced Learning Technologies (ICALT '24)}, \href{https://doi.org/10.1109/ICALT61570.2024.00033}{https://doi.org/10.1109/ICALT61570.2024.00033}
        \item[2024] \tab{} M. Misfeldt, L. Nøhr, I. Laug, V. Holm-Janas, \textbf{Z. Li}, A. Lorelei Traxler, J. Bruun, D. Spikol, and R. Müller Kristensen. \enquote{Addressing Shared Reflective Persistence Through Three Different Lenses.} \textit{pp. 199--202 in supplementary proceedings of the Sixth International Conference on Quantitative Ethnography (ICQE '24)}, \href{https://www.qesoc.org/images/pdf/ICQE24_Supplement_Proceedings.pdf}{ICQE '24 Supplementary Proceedings}
    \end{tablist}

    \subsection*{Reports and Other Publications}

    \begin{tablist}
        \item[2026] \tab{} \textbf{Z. Li}, Q. Li, S. Yamaguchi, and D. Spikol. \enquote{BadgeX: IoT-Enhanced Wearable Analytics Meets LLMs for Collaborative Learning.} \textit{arXiv preprint}, \href{https://arxiv.org/abs/2604.04093}{arXiv:2604.04093}
        \item[2022] \tab{} D. Spikol, \textbf{Z. Li}, S. Serrano-Iglesias, H. Ouhaichi, and B. Vogel. \enquote{MBOX Lightweight Voice Analysis Sensors for MMLA.} \textit{CROSSMMLA \& SLE Workshop: Learning Analytics for Smart Learning Environments Crossing Physical and Virtual Learning Spaces, LAK '22, Online, Mar 2022}, \href{https://lizaibeim.github.io/pubs/CROSSMMLA22_paper_5.pdf}{CrossMMLA @ LAK '22}
        \item[2022] \tab{} S. Serrano-Iglesias, D. Spikol, M. Bote-Lorenzo, E. Gómez-Sánchez, and \textbf{Z. Li}. \enquote{Challenges of the Adoption of MultiModal Learning Analytics in Smart Learning Environments.} \textit{CROSSMMLA \& SLE Workshop: Learning Analytics for Smart Learning Environments Crossing Physical and Virtual Learning Spaces, LAK '22, Online, Mar 2022}, \href{https://lizaibeim.github.io/pubs/CROSSMMLA22_paper_2.pdf}{CrossMMLA @ LAK '22}
    \end{tablist}

    \section*{Conference Activity}

    \subsection*{Conference Presentations\footnote{Presenting author \textit{italicized} if other than first author.}}

    \begin{tablist}
        \item[2025] \tab{} Z. Li, S. Yamaguchi, and D. Spikol. \enquote{OpenMMLA: an IoT-based Multimodal Data Collection Toolkit for Learning Analytics.} Presented at the 15th Learning Analytics and Knowledge Conference (LAK '25), Dublin, Ireland, Mar 3--7.
        \item[2024] \tab{} Z. Li, M. T. Jensen, A. Nolte, and D. Spikol. \enquote{Field report for Platform mBox: Designing an Open MMLA Platform.} Presented at the 14th Learning Analytics and Knowledge Conference (LAK '24), Kyoto, Japan, Mar 18--22.
    \end{tablist}

    \section*{Grants and Awards}

    \subsection*{Awards and Honors}

    \begin{tablist}
        \item[2026] \tab{}Meta Project Aria Research Partnership / Hardware Grant
        \item[2025] \tab{}Best Short Paper Award @ LAK '25
        \item[2017] \tab{}Wong Tit-shing Student Exchange Scholarship
    \end{tablist}

    \subsection*{Competitive Grants and Fellowships}

    \begin{tablist}
        \item[2024--2027] \tab{}PhD Fellowship, University of Copenhagen
    \end{tablist}

    \section*{Research Experience}

    \noindent \textbf{Hiroshima City University} \hfill Hiroshima, Japan \\
    \textit{Visiting Researcher} \hfill Nov 2025--Jan 2026
    \begin{list}{\textbullet}{\setlength{\leftmargin}{1.2em}
                   \setlength{\labelsep}{0.5em}
                   \setlength{\itemsep}{\listitemspace}
                   \setlength{\parsep}{\listitemspace}}
        \item Prototyped an egocentric multimodal sensing setup using mobile devices, embedded sensors, and smart glasses for real-world collaborative learning analysis.
        \item Developed CoLA, a wearable platform with an interactive AI facilitator for real-time collaborative learning analytics; established a research collaboration with Meta Project Aria.
    \end{list}
    \vspace{0.8em}

    \noindent \textbf{University of Copenhagen} \hfill Copenhagen, Denmark \\
    \textit{Doctoral Researcher} \hfill Feb 2024--Present
    \begin{list}{\textbullet}{\setlength{\leftmargin}{1.2em}
                   \setlength{\labelsep}{0.5em}
                   \setlength{\itemsep}{\listitemspace}
                   \setlength{\parsep}{\listitemspace}}
        \item Designed and developed OpenMMLA, a reusable IoT-based toolkit for multimodal data collection, synchronization, and analytics in collaborative learning environments.
        \item Built interactive pipeline components for sensor fusion, behavioral modeling, and visualization, enabling interpretable analysis of complex group interactions.
    \end{list}
    \vspace{0.8em}

    \noindent \textbf{University of Copenhagen} \hfill Copenhagen, Denmark \\
    \textit{Research Assistant} \hfill Jun 2023--Feb 2024
    \begin{list}{\textbullet}{\setlength{\leftmargin}{1.2em}
                   \setlength{\labelsep}{0.5em}
                   \setlength{\itemsep}{\listitemspace}
                   \setlength{\parsep}{\listitemspace}}
        \item Prototyped sociometric badges and AprilTag-based spatial tracking for multimodal learning analytics.
        \item Built early data collection and processing workflows for mBox, a multimodal sensing prototype that later evolved into OpenMMLA.
    \end{list}

    \section*{Teaching Experience}

    \subsection*{University of Copenhagen}

    \begin{itemize}
        \item Teaching Assistant, Introduction to Python Programming and Data Science
    \end{itemize}

    \section*{Professional Employment}

    \begin{tablist}
        \item[May 2019--Aug 2019] \tab{}Yonyou, IT Consultant, Hong Kong, China
        \item[Jun 2017--Aug 2017] \tab{}Sina.com, Data Analyst Intern, Beijing, China
    \end{tablist}

    \section*{Projects}

    \begin{itemize}
        \item \textbf{CoLA}: A wearable multimodal AI platform for egocentric sensing, real-time behavioral analysis, and interactive facilitation in collaborative learning settings, \href{https://ucph-cola.org}{\textcolor{blue}{\textit{link}}}
        \item \textbf{OpenMMLA}: An open-source IoT toolkit for multimodal data collection, synchronization, and analytics across real-world collaborative environments, \href{https://github.com/ucph-ccs/OpenMMLA}{\textcolor{blue}{\textit{link}}}
        \item \textbf{mBox}: An early multimodal sensing prototype featuring sociometric badges, audio pipelines, and AprilTag-based spatial tracking; later evolved into OpenMMLA, \href{https://github.com/ucph-ccs/mbox-uber}{\textcolor{blue}{\textit{link}}}
        \item \textbf{MMLA-Audio}: A real-time speech analytics pipeline with speaker recognition and speech overlap detection, optimized for edge deployment, \href{https://github.com/lizaibeim/mmla-audio}{\textcolor{blue}{\textit{link 1}}}, \href{https://github.com/lizaibeim/mmla-tiny-audio}{\textcolor{blue}{\textit{link 2}}}
        \item \textbf{MotionMatching}: A real-time motion matching system on Unity implemented in C\#, \href{https://github.com/lizaibeim/motion-matching}{\textcolor{blue}{\textit{link}}}
        \item \textbf{CasperFFG}: A python implementation of the CasperFFG consensus combined with PoW consensus on simulated blockchain, \href{https://github.com/lizaibeim/casper-ffg}{\textcolor{blue}{\textit{link}}}
    \end{itemize}

    \section*{Service}

    \subsection*{Academic Journal Peer Review}

    \begin{itemize}
        \item \textit{Knowledge-Based Systems}
    \end{itemize}

    \subsection*{Conference Peer Review}

    \begin{itemize}
        \item \textit{European Conference on Technology-Enhanced Learning (EC-TEL)}
    \end{itemize}

    % display today's date as Month Year after a vertical space below the end of the text
    \begin{center}
        \vfill
        Updated \monthyeardate\today
    \end{center}

\end{document}